visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-07-29 manuscript.Rmd
manuscript!

```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 item non-invariance visualization showing differences in the item intercepts and latent variable.", fig.height=8}
# plot the image for RS7
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS7", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs7-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts.", fig.height=8}
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS6", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS6), max(DF$RS6)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs6-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

Next, we would examine our replication potential for this model. Given our current results, we may not expect our intercepts to replicate. Given the order of desired steps in the  `group.equal` argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication. In our output, we do not see a loadings effect size, and this result occurs when *none* of the bootstrapped or random results are non-invariant. Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance). The intercepts show a large (i.e., close to the max possible value) non-invariant effect, $h_{nmi}$ = `r apa_num(boot.model.rs$h_nmi[1])` ($h_{mni}_p$ = `r apa_num(boot.model.rs$h_nmi_p[1])`), and therefore, we should not expect this model to show invariance in a replication.

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \@ref(tab:table-boot-effects), it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \@ref(fig:rs-partial-pic) and \@ref(fig:rs-partial-pic2) display the three plots provided in the `bootstrap_partial()` function. In general, we should expect $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(invariant) %>% pull(mean_boot_difference) %>% mean())` when items are invariant and $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(mean_boot_difference) %>% mean())` when items are not invariant. The effect size of non-invariant items ranges from $d_s$ ~ `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.

>>>>

```{r rs7-img, echo = F, include = T, size = "small", fig.cap="RS7 item non-invariance visualization showing differences in the item intercepts and latent variable."}
# plot the image for RS7
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS7", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs7-visual.png", dpi = 300, 
       width = 8, 
       height = 6,
       units = "in")
```

@@

```{r rs6-img, echo = F, include = T, size = "small", fig.cap="RS6 item non-invariance visualization similar results to RS7 with differences in item intercepts."}
plot_mi(
  data_coef = partial.rs.2$model_coef, 
  model_step = "intercepts", 
  item_name = "RS6", 
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS6), max(DF$RS6)),
  conf.level = .95, 
  model_results = partial.rs.2$invariance_models$model.intercepts,
  # which latent variable do you want 
  lv_name = "RS" 
)$complete

ggsave("figures/rs6-visual.png", dpi = 300, 
       width = 8, 
       height = 6, 
       units = "in")
```

Next, we would examine our replication potential for this model. Given our current results, we may not expect our intercepts to replicate. Given the order of desired steps in the `group.equal` argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication. In our output, we do not see a loadings effect size, and this result occurs when *none* of the bootstrapped or random results are non-invariant. Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance). The intercepts show a large (i.e., close to the max possible value) non-invariant effect, $h_{nmi}$ = `r apa_num(boot.model.rs$h_nmi[1])` ($h_{mni_p}$ = `r apa_num(boot.model.rs$h_nmi_p[1])`), and therefore, we should not expect this model to show invariance in a replication.

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \@ref(tab:table-boot-effects), it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \@ref(fig:rs-partial-pic) and \@ref(fig:rs-partial-pic2) display the three plots provided in the `bootstrap_partial()` function. In general, we should expect $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(invariant) %>% pull(mean_boot_difference) %>% mean())` when items are invariant and $M_{D}$ = `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(mean_boot_difference) %>% mean())` when items are not invariant. The effect size of non-invariant items ranges from $d_s$ \~ `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% min(., na.rm = T))` to `r apa_num(boot.partial.rs$boot_summary %>% filter(!invariant) %>% pull(d_boot) %>% max(., na.rm = T))`.

### 2024-07-29 manuscript.tex
manuscript!

Multigroup confirmatory factor analysis (MGCFA) was proposed as a method to examine differences in scale functioning across groups (Brown, 2015) using structural equation modeling and confirmatory factor analysis (CFA). The goal of MGCFA is to determine if groups are invariant or show the same response patterns on the scale. MGCFA is often performed in sequential steps to determine the location and impact of potential non-invariance. The most common procedure starts by examining overall scale structure for each group individually to show that the groups can be combined into one nested model (i.e., both models at least converge). The combined model, often described as the \emph{configural} model, creates one CFA for both groups that allows each group's estimated parameters to vary. Equality constraints between group parameters are then added sequentially to the model (Brown, 2015). If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimate should not effect overall scoring and assessment.

The first equality constraint added is usually the item factor loadings (\emph{metric} model) which requires items to be related to the latent variable at the same strength across groups. The intercepts are then constrained to be equal across groups (\emph{scalar} model) to determine the invariance of item averages. The item variances (\emph{strict} model) can then be examined to determine if the general variation in item answers are equal across groups. Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations. Non-invariance is determined by examining differences in fit indices between models with constraints versus without (Cheung \& Rensvold, 2002).

@@

If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (Byrne et al., 1989; Meredith, 1993). Similar to \emph{post hoc} follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary. If the model fit improves when groups are allowed to have separate parameter estimations, the item parameter estimate is considered non-invariant. When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups. The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness. Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups and the impact on the overall model.

@@

\emph{i} indicates an individual item, and \emph{R} indicates the reference group (Nye \& Drasgow, 2011). Therefore, an individual score is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)). Nye and Drasgow (2011) demonstrated that the terminology from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\). \(d_{MACS}\) is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for \emph{d} proposed by Cohen (2013). Therefore, if \(\tau\) or \(\lambda\) are individually (or both) different across groups, it will impact all the predicted \(X_{iR}\) scores, and thus, impact \(d_{MACS}\) values. While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing and partial invariance. In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items. Last, in line with general suggestions by Cumming (2012) and Cumming and Calin-Jageman (2016), the visualization of effect sizes in MGCFA would be an added tool for researchers to gauge the size of group differences.

@@

The \%\textgreater\% code for this manuscript can be found at \url{https://osf.io/wev5f/}. This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration. The \emph{R} package and replication/effect sizes was added after the original manuscript submission. The simulation study used to design plotting functions and test effect sizes can be found in the supplemental materials, along with worked code examples.

@@

Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results separated by bootstrapped data versus randomized data and then invariant/non-invariant outcomes. The \(d_s\) for between groups Cohen's \(d\) is included (\textbf{lakens2013?}). Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs. This dataframe should be used to determine which parameter may be different and the effect size potential between groups in a replication of the study. The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.

@@

Table \ref{tab:rs-table} indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used. Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added. The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI. If these Items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level. It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.

The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values). By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28. See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means. We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914).

Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve. The CFI for this model does meet the requirements for partial invariance, .917. The effect size is approximately the same at \(d_{MACS}\) = 0.28. See Figure \ref{fig:rs6-img} shows the difference between item intercepts and latent means.

@@

Next, we would examine our replication potential for this model. Given our current results, we may not expect our intercepts to replicate. Given the order of desired steps in the \texttt{group.equal} argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication. In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant. Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance). The intercepts show a large (i.e., close to the max possible value) non-invariant effect, and therefore, we should not expect this model to show invariance in a replication.

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant. The effect size of non-invariant items ranges from 0.43 to 0.59.

@@

In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large). While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d\) \textasciitilde{} 0.50 difference in means. While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts. The results here suggest that the effect is driven by intercepts. The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72). Given the mean standard deviation, a \(d\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale. A researcher could decide that at least \(d\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance. Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.

@@

One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles. We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena. For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population (Cha et al., 2007; Chang et al., 1999; Yu et al., 2004). The RS14 was tested in Chinese speaking samples in Chen et al. (2020) across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency. Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples. With the published data, we can use \texttt{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters. The code used for this analysis is presented in the supplemental materials.

@@

>>>>

Multigroup confirmatory factor analysis (MGCFA) was proposed as a method to examine differences in scale functioning across groups (Brown, 2015) using structural equation modeling and confirmatory factor analysis (CFA). The goal of MGCFA is to determine if groups are invariant or show the same response patterns on the scale. MGCFA is often performed in sequential steps to determine the location and impact of potential non-invariance. The most common procedure starts by examining overall scale structure for each group individually to show that the groups can be combined into one nested model (i.e., both models at least converge). The combined model, often described as the \emph{configural} model, creates one CFA for both groups that allows each group's estimated parameters to vary. Equality constraints between group parameters are then added sequentially to the model (Brown, 2015). If parameters are found to be equivalent between groups, these models are considered ``invariant'', suggesting that any subtle differences in the parameter estimates should not effect overall scoring and assessment.

The first equality constraint added is usually the item factor loadings (\emph{metric} model) which requires items to be related to the latent variable at the same strength across groups. The intercepts are then constrained to be equal across groups (\emph{scalar} model) to determine the invariance of item averages. The item variances (\emph{strict} model) can then be examined to determine if the general variation in item answers are equal across groups. Other parameter equality constraints can be set at the latent variable level (latent means, variance, covariances), but the focus is generally on the observable variables and their parameter estimations. Non-invariance is determined by examining differences in fit indices between models with constraints versus without in sequential order (Cheung \& Rensvold, 2002).

@@

If a specific step within the MGCFA testing framework shows non-invariance, partial invariance is often used to investigate where and ``how much'' invariance occurs (i.e., how many items, rather than how big the differences are Byrne et al., 1989; Meredith, 1993). Similar to \emph{post hoc} follow up tests in ANOVA, each equality constraint for that model is examined one at a time by allowing groups to vary. If the model fit improves when groups are allowed to have separate parameter estimates, the item for these groups is considered non-invariant. When only a few parameters are found that impact invariance, models are considered partially invariant, implying that most, but not all parameters are equal across groups. The researcher then interprets the impact of those items and parameters on overall scores and assessment usefulness. Partial invariance investigation is a useful tool for finding specific items that vary between groups, but does not fully explain the effect size of the difference between groups on those items and the impact on the overall model.

@@

\emph{i} indicates an individual item, and \emph{R} indicates the reference group (Nye \& Drasgow, 2011). Therefore, an individual item is predicted by the intercept of the item (\(\tau\)) added to the item loading (\(\lambda\)) times the latent variable score (\(\xi\)). Nye and Drasgow (2011) demonstrated that the terminology and equations from IRT and DIF can be used to create a measure of item functioning differences within CFA, \(d_{MACS}\). \(d_{MACS}\) is then the difference of reference group versus focal group (e.g., group 1 versus group 2) divided by a pooled standard deviation similar to formulas for \emph{d} proposed by Cohen (2013). Therefore, if \(\tau\) or \(\lambda\) are individually (or both) different across groups, it will impact all the predicted \(X_{iR}\) scores, and thus, impact \(d_{MACS}\) values. While \(d_{MACS}\) represents a necessary step for development of effect sizes within CFA, it does not separate the differences in parameters between groups in a way that can be paired with traditional MGCFA testing steps and partial invariance. In addition to the missing effect sizes at model and parameter levels, no effect size to date gives the researcher a feeling for potential replication of the invariant or non-invariant items. Last, in line with general suggestions by Cumming (2012) and Cumming and Calin-Jageman (2016), the visualization of effect sizes in MGCFA would be an added tool for researchers to gauge the size of group differences.

@@

The code for this manuscript can be found at \url{https://osf.io/wev5f/}. This tutorial was registered at \url{https://osf.io/vwf4d}, and the example provided at the end of the manuscript was added after that registration. The \emph{R} package and replication/effect sizes was added after the original manuscript submission. The simulation study used to design plotting functions and test effect sizes can be found in the supplemental materials, along with worked code examples.

@@

Next, the \texttt{boot\_summary} includes a summarized form of the bootstrapped results separated by bootstrapped data versus randomized data and then invariant/non-invariant outcomes. The \(d_s\) for between groups Cohen's \(d\) is included (Lakens, 2013). Effect sizes are only calculated when the number of bootstrapped estimates is at least 10\% of the data - therefore, you would not receive effect sizes with almost no bootstrapped runs. This dataframe should be used to determine which parameter may be different and the effect size potential between groups in a replication of the study. The \texttt{boot\_effects} table creates a summary similar to the overall model replication table based on the proportion of runs that were considered invariant versus not for each parameter.

@@

Table \ref{tab:rs-table} indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit (Cao \& Liang, 2022; Cheung \& Rensvold, 2002; Counsell et al., 2020; Jin, 2020; Putnick \& Bornstein, 2016) but for the purposes of this illustration \(\Delta\)CFI \textgreater{} .01 will be used. Table \ref{tab:rs-table} indicates that fit was degraded when the constraint on equal item intercepts was added. The code online provides an example of testing each item individually by relaxing the constraints and recalculating the CFI. If these items bring the CFI value back up to \(\Delta\)CFI \textless= .01 from the metric model, then the model would be considering partially invariant at the scalar level. It seems unlikely that the residuals will show invariance, even if partial scalar invariance can be found, as the drop in fit on the residual model is quite large.

The partial invariance results indicated that RS6 and RS7 are potential items that could be relaxed to improve model fit and create a partial scalar invariant model (i.e., by picking the largest CFI values). By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28. See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means. We repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914). Again, we see about a half-point difference between our clinical and student samples for item 6, which is about drive to achieve. The CFI for this model does meet the requirements for partial invariance, .917. The effect size is approximately the same at \(d_{MACS}\) = 0.28. See Figure \ref{fig:rs6-img} shows the difference between item intercepts and latent means.

@@

Next, we would examine our replication potential for this model. Given our current results, we may not expect our intercepts to replicate. Given the order of desired steps in the \texttt{group.equal} argument, the boot function will select the first non-invariant step (as defined by the user) in the calculation of the effect size for potential replication. In our output, we do not see a loadings effect size, and this result occurs when \emph{none} of the bootstrapped or random results are non-invariant. Therefore, we would expect the loadings to replicate (and the effect size would be 0 difference between bootstrapped and random, both showing invariance). The intercepts show a large (i.e., close to the max possible value) non-invariant effect, \(h_{nmi}\) = 3.05 (\(h_{mni_p}\) = 0.97), and therefore, we should not expect this model to show invariance in a replication.

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant. The effect size of non-invariant items ranges from \(d_s\) \textasciitilde{} 0.43 to 0.59.

@@

In summary, if one were planning a replication, the prediction would be that item intercepts would likely not replicate, with a large effect size (i.e., it is easy to judge \(h_{nmi_p}\) close to the max of one as large). While this study found partial invariance by relaxing constraints on two individual items, bootstrapped partial invariance indicates that any item could potentially be problematic with an effect size averaging \(d_s\) \textasciitilde{} 0.50 difference in means. While \(d_{MACS}\) values represented a ``small'' effect based on previous publications, this effect may be muted by examining both loadings and intercepts. The results here suggest that the effect is driven by intercepts. The overall average score on items is high: \(M_M\) = 5.04 (\(M_{SD}\) = 1.72). Given the mean and standard deviation, a \(d_s\) \textasciitilde{} 0.50 represents 0.86 or nearly one whole point on the scale. A researcher could decide that at least \(d_s\) = 0.33 or at least a third of a standard deviation would be an important change and set that as their smallest effect size of interest for invariance replication and extension. Further, a newly planned study should investigate what variables may predict when and why samples separate into bimodal representations for item means.

@@

One benefit of the open science movement on scale development is the publication of datasets or covariance tables with published articles. We can extend our examination of potential replication on other variables that may effect assessment of underlying phenomena. For example, scale translation across languages is not only impacted by the literal conversion of concepts from one language to another, but also the cultural and societal norms of the target population (Cha et al., 2007; Chang et al., 1999; Yu et al., 2004). The RS14 was tested in Chinese speaking samples in Chen et al. (2020) across five different large samples and determined that the scale showed good psychometric properties for use within Chinese speaking samples as a one-factor model of resiliency. Given these results, another researcher may assume that the models would be comparable between English speaking (i.e., likely United States) and Chinese speaking samples. With the published data, we can use \emph{visualizemi} to determine if the RS14 is invariant across language/culture, and if the results would likely replicate if tested on a new set of samples, and what, if any, effect size differences are found in parameters. The code used for this analysis is presented in the supplemental materials.

@@

\bibitem[\citeproctext]{ref-lakens2013}
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}. \url{https://doi.org/10.3389/fpsyg.2013.00863}
